Flatiron cleaning

### 2023-01-06 Rmd/Response to reviewers.Rmd

tbl2 <- normal %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- normal %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl4 <- overweight %>%
  filter(therapy == "Upfront Chemo")
tbl41 <- 
  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
             event = tbl4$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl4) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- overweight %>%
  filter(therapy == "Upfront Surgery")
tbl51 <- 
  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
             event = tbl5$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl5) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

a <- tbl_merge(list(tbl21, tbl41), tab_spanner = c("Underweight and normal weight", "Overweight or obese"))
b <- tbl_merge(list(tbl31, tbl51))
tbl_stack(list(a, b),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

## Association with BMI
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`  
stratified by therapy  
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ bmi_cat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ bmi_cat + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

Overall
```{r}
coxph(Surv(time = Frontline$month_at_os_from_treatment, 
             event = Frontline$vital_status) ~ bmi_cat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  Frontline) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
```

***

```{r echo=FALSE, out.width='30%'}
knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
```
